Analysis for Project

### 2021-11-22 analysis/analysis.Rmd
Add better variable headers in descriptive stats table

```{r retention-by-year}
acs %>%
  group_by(year) %>%
  summarize(below_grade=mean(below_exp_grade)) %>%
  ggplot(aes(x=year, y=below_grade))+
  geom_line()+
  geom_point()+
  scale_x_continuous(breaks=c(2010,2014,2018))+
  scale_y_continuous(labels=scales::percent)+
  labs(x="current grade", y="percent clearly behind grade level for age")+
  theme_bw()
```

@@

tbl_summary %>%
  mutate_if(is.numeric, format, big.mark=",") %>%
  kbl(caption="Descriptive statistics by race. Shading indicates biracial group. Groups ordered by sample size.", align = c("l",rep("r", ncol(tbl_summary)-1))) %>%
  kable_paper() %>%
  row_spec(index_biracial, background = "#D3D3D3")
```

>>>>

```{r retention-by-year}
acs %>%
  group_by(year) %>%
  summarize(below_grade=mean(below_exp_grade)) %>%
  ggplot(aes(x=year, y=below_grade))+
  geom_line()+
  geom_point()+
  geom_smooth(se=FALSE)+
  scale_x_continuous(breaks=c(2010,2014,2018))+
  scale_y_continuous(labels=scales::percent)+
  labs(x="current grade", y="percent clearly behind grade level for age")+
  theme_bw()
```

@@

tbl_summary %>%
  mutate_if(is.numeric, format, big.mark=",") %>%
  kbl(caption="Descriptive statistics by race. Shading indicates biracial group. Groups ordered by sample size.",
      align = c("l",rep("r", ncol(tbl_summary)-1)),
      col.names=c("race","n","% below expected grade", "mean age",
                  "% foreign-born","% speak English well",
                  "% Both parents speak english well","% either parent foreign-born",
                  "mean family income","% own home","% either parent, HS diploma",
                  "% Either parent, BA degree","% parents married")) %>%
  kable_paper() %>%
  row_spec(index_biracial, background = "#D3D3D3")
```
